### 2024-05-31 slides/estimation.tex
rearranging

    \begin{equation*}
        \text{\textit{kaitz}}_{ct}(\rho) \equiv \log{w^{\text{\textit{min}}}_{ct}} - \log{w^{\rho}_{ct}}
    \end{equation*}
    with 
    \begin{equation*}
        w^{\rho}_{ct} = \sum_{i\in c} \dfrac{e_i}{E_c}\,w^{\rho}_{it} \quad\text{and}\quad w^{\rho}_{it} = \sum_{o\in i} \dfrac{e_o}{E_i}\,w^{\rho}_{oit}
    \end{equation*}
    and
    \vspace{9pt}
    \begin{wideitemize}
        \item[\textcolor{fblu}{\textbullet}] \(\textcolor{fblu}{w^{\text{\textit{min}}}_{ct}}\): minimum wage in county \(\textcolor{fblu}{c}\) at time \(\textcolor{fblu}{t}\), \(\textcolor{fblu}{w^{\rho}_{ct}}\): wage percentile \(\textcolor{fblu}{\rho}\)
        \item[\textcolor{fblu}{\textbullet}] \(\textcolor{fblu}{w^{\rho}_{cit}}\): wage percentile in occupation \(\textcolor{fblu}{o}\) in industry \(\textcolor{fblu}{i}\) at time \(\textcolor{fblu}{t}\) 
        \item[\textcolor{fblu}{\textbullet}] \(\textcolor{fblu}{e_o}\): share of employment of occupation \(\textcolor{fblu}{o}\) in industry \(\textcolor{fblu}{i}\), \(\textcolor{fblu}{e_i}\): share of county employment in industry \(\textcolor{fblu}{i}\)
    \end{wideitemize}

@@

    \begin{center}
        \includegraphics[scale=0.4]{mop010unemprate.png}
    \end{center}

    \hyperlink{perc_comparison_1}{\beamerbutton{Percentiles comparison}}
    \hyperlink{dist_1}{\beamerbutton{Distributions}}

@@

    \label{unemp_result}
    \frametitle{Results} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

    \begin{center}
        \includegraphics[scale=0.4]{mop010unemp.png}
    \end{center}

    \hyperlink{perc_comparison_2}{\beamerbutton{Percentiles comparison}}
    \hyperlink{dist_2}{\beamerbutton{Distributions}}

@@

    \label{emp_result}
    \frametitle{Results} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

    \begin{center}
        \includegraphics[scale=0.4]{mop010emp.png}
    \end{center}

    \hyperlink{perc_comparison_3}{\beamerbutton{Percentiles comparison}}
    \hyperlink{dist_3}{\beamerbutton{Distributions}}

    \label{labforce_result}
    \frametitle{Results} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

    \begin{center}
        \includegraphics[scale=0.4]{mop010labforce.png}
    \end{center}

    \hyperlink{perc_comparison_4}{\beamerbutton{Percentiles comparison}}
    \hyperlink{dist_4}{\beamerbutton{Distributions}}

>>>>

    \begin{equation*}
        \text{\textit{kaitz}}_{ct}(\rho) \equiv \log{w^{\text{\textit{min}}}_{ct}} - \log{w^{\rho}_{ct}}
    \end{equation*}
    with 
    \begin{equation*}
        w^{\rho}_{ct} = \sum_{i\in c} \dfrac{e_i}{E_c}\,w^{\rho}_{it} \quad\text{and}\quad w^{\rho}_{it} = \sum_{o\in i} \dfrac{e_o}{E_{it}}\,w^{\rho}_{oit}
    \end{equation*}
    and
    \vspace{9pt}
    \begin{wideitemize}
        \item[\textcolor{fblu}{\textbullet}] \(\textcolor{fblu}{w^{\text{\textit{min}}}_{ct}}\): minimum wage in county \(\textcolor{fblu}{c}\) at time \(\textcolor{fblu}{t}\), \(\textcolor{fblu}{w^{\rho}_{ct}}\): wage percentile \(\textcolor{fblu}{\rho}\)
        \item[\textcolor{fblu}{\textbullet}] \(\textcolor{fblu}{w^{\rho}_{cit}}\): wage percentile in occupation \(\textcolor{fblu}{o}\) in industry \(\textcolor{fblu}{i}\) at time \(\textcolor{fblu}{t}\) 
        \item[\textcolor{fblu}{\textbullet}] \(\textcolor{fblu}{e_o}\): share of employment of occupation \(\textcolor{fblu}{o}\) in industry \(\textcolor{fblu}{i}\), \(\textcolor{fblu}{e_i}\): share of county employment in industry \(\textcolor{fblu}{i}\)
    \end{wideitemize}

@@

    \begin{center}
        \includegraphics[scale=0.4]{mop10_unemp_rate.png}
    \end{center}

    \hyperlink{perc_comparison_1}{\beamerbutton{Percentiles comparison}}
    \hyperlink{ta_1}{\beamerbutton{Time average}}

@@

    \label{emp_rate_result}
    \frametitle{Results} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

    \begin{center}
        \includegraphics[scale=0.4]{mop10_emp_rate.png}
    \end{center}

    \hyperlink{perc_comparison_2}{\beamerbutton{Percentiles comparison}}
    \hyperlink{ta_2}{\beamerbutton{Time average}}

@@

    \label{lab_force_rate_result}
    \frametitle{Results} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

    \begin{center}
        \includegraphics[scale=0.4]{mop10_lab_force_rate.png}
    \end{center}

    \hyperlink{perc_comparison_3}{\beamerbutton{Percentiles comparison}}
    \hyperlink{ta_3}{\beamerbutton{Time average}}
